\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2018-01-08 eg6-letters/NIM/review-1/review-1.tex

\subsection*{Chapter 2}
\item As already said I would not speak of cylindrical GEMs but 
   semi-cylindrical. Moreover, please add the reference to Sauli's paper [11] 
   when speaking the first time about GEM in the text.\\
\textcolor{blue}{cylinderical GEMs-> semi-cylinderical. The reference has been added.}

\item In my opinion, this chapter should highlight better which are the 
   improvements w.r.t. BoNuS detector to underline the originality of this 
   work. For example, better acceptance? Higher gain? Higher electric 
   stability? Lower material budget? Please quote some old and new values, 
   maybe in a table, to make them evident.\\
\textcolor{red}{To the group: Do we have such a comparison? }

\item Relevant length and thicknesses of the various elements are reported in 
   the text and in the figure, can you please add also the z position of the 
   target w.r.t the detector? To give the complete information, I would also 
   add the value of the induction gap electric field, which is the only missing 
   field value and the value of the reached amplification gain with the three 
   GEM.\\
\textcolor{blue}{ The text has been modified to clarify the z position of the 
target and the RTPC with respect to CLAS sectrometer.\\}
\textcolor{red}{- Regarding the electric field in the induction gap, it was 2.8 
kV/cm in BoNuS, does anyone know our exact field in this gap?\\}
\textcolor{blue}{- The gain of such GEM configuration has been studied by 
   CERN's Gas Detector Development Group (Fabio Sauli, Progress with the Gas 
   Electron Multiplier, 2nd Workshop on Advanced Transition Radiation Detectors 
   for Accelerator and Space Applications (Bari, Sept. 4-7, 2003), Nucl. Instr. 
   and Meth. A522(2004)93). The results, see the reference, demonstrate that 
one should not simply add gains to each other for multilayer GEM 
amplifications.  We did not evaluate precisely the overall gain in our chamber, 
so we do not have a value for our RTPC GEM system at this point.}

@@

\subsection*{ Chapter 4}
	/paragraph 4.1
\item I would really prefer to call it drift "velocity" instead of drift 
   "speed"\\
\textcolor{red}{To the group: We do have radial and azimuthal drift velocities, 
but we measure the average of their sum. }

\item I don't really understand the procedure to find the drift velocity 
   described here and fig. 7. What is $Nb_{max}$ and $Nb_{max/2}$? Why does 
   $T_{max/2}$ correspond to $Nb_{max/2}$ and why is it used as $T_{max}$? If I 
   make a quick calculation and use $T_{max}$ ~ 65 * 100ns and a drift length 
   of ~ 3cm /cos(23$^{\circ}$) ~ 7.5 cm I get a $v_{drift}$ ~ 1.15 cm/microsec 
   << 5 cm/microsec which is the average value of drift velocity in drift 
   chambers.\\
The procedure according to me would be:\\
- for each hit associated to a track, whose time information is available, take 
the drift time $t_{drift_{i}}$;\\
- plot the distribution of these $t_{drift_{i}}$;\\
- find the $T_{min}$ = minimum $t_{drift_{i}}$ and $T_{max}$ = maximum 
$t_{drift_{i}}$\\
- compute $delta_{t} = T_{max} - T_{min}$ and extract the drift velocity by 
dividing the track length / $delta_{t}$. Figure 8 would have the $delta_{t}$ 
instead of the $T_{max}$ vs z.\\
Please provide more details on the applied procedure, since I have the open 
questions I wrote before and I could not understand it properly. Moreover, 
please quote the value of the found drift velocity. Is it in accordance with 
the simulations?\\
\textcolor{red}{- The text has been updated to clarify the procedures.\\
                - With T = 65*100~ns and drift length equal to 3cm/ 
             cos(23$^{\circ}$, $v_{drift}$ = 0.501 cm/microsec which is 
          consistent with our 0.61 cm/microsec from simulation. \\
               - In deed, we use $delta_{t} = T_{max/2} - T_{min}$ in our 
            reconstruction code.}

>>>>

\subsection*{Chapter 2}
\item As already said I would not speak of cylindrical GEMs but 
   semi-cylindrical. Moreover, please add the reference to Sauli's paper [11] 
   when speaking the first time about GEM in the text.\\
\textcolor{blue}{cylindrical GEMs-> semi-cylindrical. The reference has been added.}

\item In my opinion, this chapter should highlight better which are the 
   improvements w.r.t. BoNuS detector to underline the originality of this 
   work. For example, better acceptance? Higher gain? Higher electric 
   stability? Lower material budget? Please quote some old and new values, 
   maybe in a table, to make them evident.\\
\textcolor{blue}{The main difference is in the design of the structure, this has 
been made clearer in this chapter.}

\item Relevant length and thicknesses of the various elements are reported in 
   the text and in the figure, can you please add also the z position of the 
   target w.r.t the detector? To give the complete information, I would also 
   add the value of the induction gap electric field, which is the only missing 
   field value and the value of the reached amplification gain with the three 
   GEM.\\
\textcolor{blue}{ The text has been modified to clarify the z position of the 
target and the RTPC with respect to CLAS sectrometer.\\}
\textcolor{red}{- Regarding the electric field in the induction gap, it was 2.8 
kV/cm in BoNuS, does anyone know our exact field in this gap?\\}
\textcolor{blue}{- The gain of such GEM configuration has been studied by 
   CERN's Gas Detector Development Group (Fabio Sauli, Progress with the Gas 
   Electron Multiplier, 2nd Workshop on Advanced Transition Radiation Detectors 
   for Accelerator and Space Applications (Bari, Sept. 4-7, 2003), Nucl. Instr. 
   and Meth. A522(2004)93). The results, see the reference, demonstrate that 
one should not simply add gains to each other for multilayer GEM 
amplifications.  We did not evaluate precisely the overall gain in our chamber, 
so we do not have a value for our RTPC GEM system at this point.}
>>>>>>> 10849ae3d4920c417e2d8b634ec1b3e86ec0ad03

@@

\subsection*{ Chapter 4}
	/paragraph 4.1
\item I would really prefer to call it drift "velocity" instead of drift 
   "speed"\\
\textcolor{red}{To the group: We do have radial and azimuthal drift velocities, 
but we measure the average of their sum. Raph: What is the link with the question?}

\item I don't really understand the procedure to find the drift velocity 
   described here and fig. 7. What is $Nb_{max}$ and $Nb_{max/2}$? Why does 
   $T_{max/2}$ correspond to $Nb_{max/2}$ and why is it used as $T_{max}$? If I 
   make a quick calculation and use $T_{max}$ ~ 65 * 100ns and a drift length 
   of ~ 3cm /cos(23$^{\circ}$) ~ 7.5 cm I get a $v_{drift}$ ~ 1.15 cm/microsec 
   << 5 cm/microsec which is the average value of drift velocity in drift 
   chambers.\\
The procedure according to me would be:\\
- for each hit associated to a track, whose time information is available, take 
the drift time $t_{drift_{i}}$;\\
- plot the distribution of these $t_{drift_{i}}$;\\
- find the $T_{min}$ = minimum $t_{drift_{i}}$ and $T_{max}$ = maximum 
$t_{drift_{i}}$\\
- compute $delta_{t} = T_{max} - T_{min}$ and extract the drift velocity by 
dividing the track length / $delta_{t}$. Figure 8 would have the $delta_{t}$ 
instead of the $T_{max}$ vs z.\\
Please provide more details on the applied procedure, since I have the open 
questions I wrote before and I could not understand it properly. Moreover, 
please quote the value of the found drift velocity. Is it in accordance with 
the simulations?\\
\textcolor{red}{- The text has been updated to clarify the procedures.\\
                - With T = 65*100~ns and drift length equal to 3cm/ 
             cos(23$^{\circ}$, $v_{drift}$ = 0.501 cm/microsec which is 
          consistent with our 0.61 cm/microsec from simulation. \\
               - In deed, we use $delta_{t} = T_{max/2} - T_{min}$ in our 
            reconstruction code.} 
>>>>>>> 10849ae3d4920c417e2d8b634ec1b3e86ec0ad03
